A framework for mentored data science research projects

### 2019-11-11 Rmd/methods.Rmd
updated ms

Our framework broadens statistical computing by including the emerging areas of
social media data analysis, sentiment analysis, and topic modeling. 
Both of our students used Twitter tweets, which we accessed through a Twitter 
streaming API.

@@

Students wrote code to parse and organize tweet JSONs. Each tweet's JSON included required fields, and, possibly, some optional fields. The required fields are:

@@

>>>>

Our framework broadens statistical computing by including the emerging areas of
social media data analysis, sentiment analysis, and topic modeling. 
Both students used Twitter tweets, which we accessed through a Twitter 
streaming API.

@@

Students wrote code to parse and organize tweet JSONs. They organized their R code into a package, https://github.com/rturn/parseTweetFiles. 
Each tweet's JSON included required fields, and, possibly, some optional fields. 
The required fields are:

@@

Both mentored students combined computing with data analysis in the practice of statistics. They used a combination of latent dirichlet allocation topic modeling, sentiment analysis, and time series analysis to reach conclusions about real world data.

Both drew heavily on our collection of tweets. One student examined Standard and Poor's 500 index daily 
closing prices over time. She also analyzed sentiments from each day's stock market-related tweets 
to look for relationships between tweet sentiment and stock market prices.

Our other student focused on developing detection methods for social media events through 
topic modeling of tweets at different time periods. As a proof of principle, he fitted topic 
models to collections of tweets preceding, during, and following the National Football 
League's Super Bowl game. He hypothesized that topics would evolve over time, with football-related tweets appearing during the football game and disappearing soon after conclusion of the game.
